---
title: "Shiny Server Droplet"
author: "Zac Garland"
date: "11/18/2019"
output:
  rmarkdown::html_document:
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = F)
```

run `r puttygen`

accept defaults

generate


save private key

copy public key into droplet

change hostname

create droplet

### namecheap

custom DNS

change nameservers to digital ocean

### digital ocean

add domain


add A record @ direct to server IP
use 300 TTL and then change after 24 hours

create CNAME record * as an alias of @

create CNAME record www as an alias of @

### Putty

add digital ocean ip address to putty

port 22 

ssh connection

left sidebar: 

SSH > Auth > browse key .ppk

connection > data > auto-login username root

go back to session, give it a name, save, then open

```{r}
adduser shiny

gpasswd -a shiny sudo

adduser zac

gpasswd -a zac sudo

su - zac

```




# install nginx

```{r}
sudo apt-get update
sudo apt-get -y install nginx
```


# install R

```{r}
sudo sh -c 'echo "deb http://cran.rstudio.com/bin/linux/ubuntu bionic-cran35/" >> /etc/apt/sources.list'

gpg --keyserver keyserver.ubuntu.com --recv-key E298A3A825C0D65DFD57CBB651716619E084DAB9
gpg -a --export E298A3A825C0D65DFD57CBB651716619E084DAB9 | sudo apt-key add -

  
sudo apt-get update
sudo apt-get -y install r-base  


R
q()
  
```


add swap space

```{r}
sudo /bin/dd if=/dev/zero of=/var/swap.1 bs=1M count=1024
sudo /sbin/mkswap /var/swap.1
sudo /sbin/swapon /var/swap.1
sudo sh -c 'echo "/var/swap.1 swap swap defaults 0 0 " >> /etc/fstab'
```


install devtools

```{r}
sudo apt-get -y install libcurl4-gnutls-dev libxml2-dev libssl-dev
sudo su - -c "R -e \"install.packages('devtools', repos='http://cran.rstudio.com/')\""
```



install R Studio Server

check which version of Ubuntu

https://rstudio.com/products/rstudio/download-server/debian-ubuntu/

```{r}

lsb_release -a

```


```{r}
sudo apt-get install gdebi-core
wget https://download2.rstudio.org/server/bionic/amd64/rstudio-server-1.2.5019-amd64.deb
sudo gdebi rstudio-server-1.2.5019-amd64.deb
```



install shiny sever

```{r}
sudo su - -c "R -e \"install.packages('shiny', repos='http://cran.rstudio.com/')\""
sudo su - -c "R -e \"install.packages('rmarkdown', repos='http://cran.rstudio.com/')\""

wget https://download3.rstudio.org/ubuntu-14.04/x86_64/shiny-server-1.5.12.933-amd64.deb
sudo gdebi shiny-server-1.5.12.933-amd64.deb
```


add permissions

```{r}
sudo groupadd shiny-apps
sudo usermod -aG shiny-apps zac
sudo usermod -aG shiny-apps shiny
cd /srv/shiny-server
sudo chown -R zac:shiny-apps .
sudo chmod g+w .
sudo chmod g+s .
```



install git and tell it who you are

```{r}
sudo apt-get -y install git
git config --global user.email "zachary.garland@outlook.com"
git config --global user.name "zac-garland"

cd /srv/shiny-server
git init


```



go to github and create new repo


```{r}
git remote add origin https://github.com/zac-garland/shiny-server.git
git add .
git commit -m "Initial commit"
git push -u origin master
```




#nginx config

make a backup
```{r}
cd

sudo cp /etc/nginx/sites-enabled/default /etc/nginx/sites-enabled/default-backup
```


sign into file zilla

https://www.digitalocean.com/community/tutorials/how-to-use-filezilla-to-transfer-and-manage-files-securely-on-your-vps

make a backup of nginx config

```{r}

sudo cp /etc/nginx/sites-enabled/default /etc/nginx/sites-enabled/default-backup


```



edit /etc/nginx/sites-enabled/default

add these lines above server{


```{r}
map $http_upgrade $connection_upgrade {
  default upgrade;
  ''      close;
}
```

change server_name from _ to localhost

add these lines below
```{r}

add these lines

location /shiny/ {
  proxy_pass http://127.0.0.1:3838/;
  proxy_http_version 1.1;
  proxy_set_header Upgrade $http_upgrade;
  proxy_set_header Connection $connection_upgrade;
  rewrite ^(/shiny/[^/]+)$ $1/ permanent;
}

location /rstudio/ {
  proxy_pass http://127.0.0.1:8787/;
  proxy_http_version 1.1;
  proxy_set_header Upgrade $http_upgrade;
  proxy_set_header Connection $connection_upgrade;
}
```

https://www.digitalocean.com/community/tutorials/how-to-set-up-shiny-server-on-ubuntu-16-04

https://jasperhg90.gitbooks.io/shiny-server-series-the-complete-guide/part-3-ssl.html

ssl encryption

```{r}
cd /usr/local/sbin
sudo wget https://dl.eff.org/certbot-auto


```



certbot-auto certonly -a webroot --webroot-path=/var/www/html -d zacgarland.dev -d www.zacgarland.dev
